Joint Neighborhood Subgraphs Link Prediction

### 2017-06-30 paper.tex
F

\section{Introduction and related work}
We are witnessing a constant increase of the rate at which data is being produced and made available in machine readable formats. Interestingly it is not only the quantity of data that is increasing, but also its complexity, i.e. not only are we measuring a number of attributes or features for each data point, but we are also capturing their mutual relationships, that is, we are considering data that is non independent and identically distributed (non i.i.d.). This yields collections that are best represented as graphs or relational data bases and requires a more complex form of analysis.

>>>>

\section{Introduction and related work}
We are witnessing a constant increase of the rate at which data is being produced and made available in machine readable formats. Interestingly it is not only the quantity of data that is increasing, but also its complexity, i.e. not only are we measuring a number of attributes or features for each data point, but we are also capturing their mutual relationships, that is, we are considering non independent and identically distributed (non i.i.d.) data. This yields collections that are best represented as graphs or relational data bases and requires a more complex form of analysis. As cursory examples of domains of interest  it is sufficient to mention social networks, where nodes are people and edges encode a type of association such as friendship, bioinformatics, where nodes are proteins or metabolites and edges represent the type of chemical interaction,
